%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[english]{babel}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{hyperref}

% Adjust margins
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}

% Font
% Uncomment one of the following font packages if desired
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}
%\usepackage{CormorantGaramond}
%\usepackage{charter}

% Page styling
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% URL style
\urlstyle{same}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Heading
\begin{center}
    \textbf{\Huge \scshape Advait Jadhav} \\
    \small  +91 \textbf{91370} \textbf{63788} $|$ \href{https://advtszn.xyz}{\underline{Portfolio}} $|$ \href{mailto:hey@advtszn.xyz}{\underline{hey@advtszn.xyz}} $|$ 
    \href{https://linkedin.com/in/advtszn}{\underline{linkedin.com/in/advtszn}} $|$
    \href{https://github.com/advtszn}{\underline{github.com/advtszn}}
\end{center}

% Career Objective

% Experience
\section{Experience}
\resumeItemListStart
  \resumeSubheading
    {Software Developer (Full-stack)}{November 2025 -- Present}
    {WLDD Private Limited}{Remote}
    \resumeItemListStart
      \resumeItem{Develop backend systems for \textit{Solo} and \textit{Memed}, building production APIs, \textbf{internal workflows}, and admin functionalities for campaign management and creator operations.}
      \resumeItem{Built core backend services for \textit{Listable Labs}, implementing \textbf{AI evaluation pipelines} and \textbf{asynchronous job processing}.}
      \resumeItem{Own development of the \textit{ScoopWhoop} platform revamp, building backend, public website and internal CMS.}
      \resumeItem{Built internal services like \textit{DataDaddy}, a unified API for social media scraping services and enhanced legacy video matching service by introducing \textbf{audio fingerprinting} using spectral peak analysis.}
      \resumeItem{\textbf{Tech used:} TypeScript, Python, Express.js, MongoDB, Next.js, React.js}
    \resumeItemListEnd
\resumeItemListEnd

\resumeItemListStart
  \resumeSubheading
    {Freelance Software Engineer}{May 2025 -- September 2025}
    {Stealth Startup}{Remote}
    \resumeItemListStart
      \resumeItem{Independently developed an automated, multilingual crypto news aggregation platform.}
      \resumeItem{Designed an \textbf{ETL pipeline} that aggregated headlines from 5+ news sources, processing \textbf{50--75 articles daily}.}
      \resumeItem{Built an \textbf{event-driven backend} using BullMQ to orchestrate \textbf{LLM-based article generation}, translation, and automated publishing to both the website and Telegram channel.}
      \resumeItem{\textbf{Tech used:} TypeScript, Python, Astro, Hono, BullMQ, Redis, Docker}
    \resumeItemListEnd
\resumeItemListEnd

\resumeItemListStart
  \resumeSubheading
    {Full-stack Engineer}{May 2024 -- June 2025}
    {WNE3}{Remote}
    \resumeItemListStart
      \resumeItem{Developed full-stack features for \textit{TOBE}, a \textbf{GenAI-powered print-on-demand platform}, including merchant dashboards and internal tooling.}

    \resumeItem{Built a \textbf{prompt enhancement and classification service} that transformed user requests into structured prompts by identifying apparel types and design categories for downstream image generation.}
    
    \resumeItem{Implemented the initial \textbf{merchandise generation pipeline} and contributed to the first end-to-end product prototype used for investor pitches.}
      \resumeItem{\textbf{Tech used:} TypeScript, Python, FastAPI, Next.js, Docker}
    \resumeItemListEnd
\resumeItemListEnd



% Projects
\section{Projects}
\resumeItemListStart
  \resumeProjectHeading{\textbf{IndieLettr} $|$ \emph{NextJS, TypeScript, SQLite}}{\href{https://indielettr.com}{\textit{View Project}}}
    \resumeItemListStart
      \resumeItem{Indielettr is a \textbf{newsletter creation and management platform} focused towards email marketing for indie creators and small business owners.}
      \resumeItem{\textbf{Co-founded} \& \textbf{Solo-developed} the platform during Buildspace nights \& weekends s5.}
    \resumeItemListEnd
\resumeItemListEnd
\resumeItemListStart
  \resumeProjectHeading{\textbf{CreatorDaddy} $|$ \emph{TypeScript, Next.js, ChromaDB, Vercel AI SDK}}{\href{https://github.com/advtszn/creator-daddy}{\textit{View Project}}}
    \resumeItemListStart
      \resumeItem{Built a proof-of-concept ETL and semantic search pipeline that scraped creator content, generated embeddings, and indexed them in ChromaDB for natural-language creator discovery.}
      \resumeItem{Designed a hybrid retrieval architecture combining vector search with structured creator metadata (e.g., location, follower count, niche) to support intelligent creator recommendations.}
    \resumeItemListEnd
\resumeItemListEnd

% Education
\section{Education}
\resumeItemListStart
  \resumeSubheading
    {Vidyalankar Polytechnic}{Wadala, Mumbai}
    {Diploma in \textbf{Computer Engineering} | Passed with \textbf{90.12\%}}{2023 - 2026}
\resumeItemListEnd
\resumeItemListStart
  \resumeSubheading
    {All Saints High School}{Kalyan, Thane}
    {CBSE | Passed with \textbf{94\%}}{2017 - 2023}
\resumeItemListEnd

% Technical Skills
\section{Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} TypeScript, JavaScript, Python}
  \resumeItem{\textbf{Backend:} Node.js, Express.js, Hono, FastAPI, tRPC}
  \resumeItem{\textbf{Frontend:} Next.js, React.js, Astro, TanStack Query}
  \resumeItem{\textbf{Databases:} MongoDB, Redis, SQLite, ChromaDB}
  \resumeItem{\textbf{Infrastructure:} Docker, BullMQ, Git}
\resumeItemListEnd

\end{document}